\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-09 Response.tex

In addition,~\Cref{prop:config_error} was modified to include additional detail on the notation \( \dirDiff{f}{x}\) as
\begin{correction}
The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
	\end{align}
	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
	\end{correction}

\item \textit{This is serious. In~\cref{sec:attitude_control}, the upper bounds listed in~\cref{prop:eR_dot_bound} are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in~\cref{prop:adaptive_control}, the stability proof under the proposed controller is far from complete.}

The stability proof has been improved and several modifications have been included in the manuscript:
\begin{itemize}
    \item An additional quadratic property has been derived for \( \Psi \) and shown in~\cref{prop:config_error},
    \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
    \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
\end{itemize}

The revised manuscript, through~\cref{prop:config_error,prop:adaptive_control}, demonstrates several properties of the error function and the error variables which are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.  Later in the stability proof of~\cref{prop:adaptive_control}, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.  As $D$ is an open neighborhood of the desired attitude, the revised manuscript completes the stability proof.

\item \textit{Typo in~\cref{eqn:c_bound}}
